---
title: "ObsMarkRecapture"
author: "Toon Van Daele"
date: "1 september 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MetaLandSim)
library(plyr)
library(dplyr)
library(ggplot2)
library(pander)
library(RMark)
```


```{r loading data}

# Loading all population data
# Output from IBM model

df.pop <- read.csv2("c:/temp/output.txt", sep = ",")
str(df.pop)
summary(df.pop)
```


# Properties and parameters of the population

Number of patches:  `r dplyr::n_distinct(df.pop$patch)`

Number of timesteps: `r dplyr::n_distinct(df.pop$timestep)`

Number of unique individuals:  `r dplyr::n_distinct(df.pop$ID)`



# Simple CJS observation proces

- Constant detection probability (i.e. not dependent on time, density, patch, ...)

- other assumptions...


## Mark recapture properties CJS model

```{r}
p <- 0.8  # Detection probability

EncTime <- c(20,21,22,23,24,25,26,27,28,29) # Encounter timesteps
```

Detection probability `r p`

Encounter timesteps `r EncTime`


```{r}

df.EncHistFlat <- data.frame()

for (i in EncTime) {
  
  df.mark <- df.pop %>%
    dplyr::filter(timestep == i, age > 1) %>%
    dplyr::sample_frac(p, replace = FALSE) %>%
    select(timestep, ID)
  df.mark$Occ <- 1
  df.EncHistFlat <- rbind(df.EncHistFlat, df.mark)
}

str(df.EncHistFlat)

df.EncHist <- df.EncHistFlat %>%
  tidyr::spread(timestep, Occ, fill = 0) %>%
  tidyr::unite(ch, 1:length(EncTime) + 1, sep = "") %>%
  dplyr::select(ch)

  
df.EncHist

CJS.Phidot.pdot <- mark(data = df.EncHist)


```



